---
title: "dataquieR report"
author: "`r library(dataquieR); if (exists('report') && length(report$author) == 1 && is.character(report$author)) report$author else prep_get_user_name()`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  flexsiteboard::flex_site_board:
    self_contained: false
    storyboard: false
    vertical_layout: "scroll"
    orientation: "columns"
  flexdashboard::flex_dashboard:
    self_contained: true
    storyboard: false
    vertical_layout: "scroll"
    orientation: "columns"
  html_document:
    toc: true
    toc_depth: 2
---
```{r echo=FALSE}
# warning <- function(...) {
  # print("WARNING")
  # print(knitr::opts_current$get()$label)
  # print(tryCatchLog::get.pretty.call.stack(call.stack = sys.calls()))
  # print("/WARNING")
#}
```

```{css}
/*.chart-wrapper { overflow-x: scroll; }*/
```

```{r echo=FALSE, include=FALSE}
knitr::knit_meta_add(list(rmarkdown::html_dependency_font_awesome()))
```


```{r setup, include=FALSE}
if (!exists("params")) { params <- list() }
params$debug <- FALSE
if (params$debug) {
  template <- "default"
  packageName <- "dataquieR"
  chunk_echo <- FALSE
  chunk_warning <- FALSE
  chunk_error <- FALSE
  chunk_message <- FALSE
  progress <- function(...) { invisible(NULL) }
  load("/tmp/report.RData")
}

variables <- report$app_mat$SummaryTable$Variables

df_report <- as.data.frame(report)
if (nrow(df_report) * ncol(df_report) == 0)
  stop("Report is empty, no results at all.")
library(DT)
datatable(data.frame(a = 1, b = Sys.time(), c = "test", d = 1.1, 
                     e = as.factor("test"), stringsAsFactors = FALSE),
          filter = "top")
knitr::opts_chunk$set(echo = chunk_echo, warning = chunk_warning, error = chunk_error, message = chunk_message)
cache <- new.env(parent = emptyenv())
process_result_chunk <- function(iform, outputSlot, title, subreport, variable, by_indicator = FALSE) {
    subreport <- match.arg(subreport, c("", "mv", "table", "plotlist_not_mv", "meta_miss"))
    if (nchar(subreport) > 0)
      subreport <- paste0("_", subreport)
    current_results <- subset(df_report, implementationform == iform, 'results', drop = TRUE)
    resp_vars <- subset(df_report, implementationform == iform, 'resp_vars', drop = TRUE)
    call_meta <- 
      subset(df_report, 
             implementationform == iform, 
             setdiff(colnames(df_report), "results"), drop = TRUE)
    
    child_hash <-
      digest::digest(list(
        iform, outputSlot, title, subreport, variable, by_indicator
      ))
    
    if (exists(child_hash, cache)) {
      return(get(child_hash, cache))
    }
    
    if (by_indicator && subreport == "_table" && outputSlot == "SummaryTable") {
      chunk <- subset(current_results, resp_vars == variable, outputSlot)
      class(chunk) <- union(class(chunk), "SummaryTable_by_indicator")
    } else {
      chunk <- suppressWarnings(suppressMessages(try(
        knitr::knit_child(
          system.file(sprintf("%s_subreport%s.Rmd", template, subreport), package = packageName), 
          envir = environment(), 
          quiet = TRUE,
          options = list( # https://rdrr.io/github/rubenarslan/formr/man/asis_knit_child.html
             fig.path = paste0(knitr::opts_chunk$get("fig.path"), child_hash, "-"), 
             cache.path = paste0(knitr::opts_chunk$get("cache.path"), child_hash, "-")
          )
        ), 
      silent = TRUE)))
      chunk <- paste(chunk, collapse = "\n")
      if (nchar(chunk) < 400 && grepl(
          "^Error .*: No results here$",
          chunk, perl = TRUE)) {
        chunk <- ""
      }
      chunk <- paste0("\n<!-- template='", 
                      sprintf("%s_subreport%s.Rmd", template, subreport), 
                      "' -->\n", chunk)
    }
    
    assign(child_hash, chunk, cache)

    return(chunk)
}
call_plan <- dplyr::tribble(
  ~ iform, ~ outputSlot, ~ title, ~ subreport,
#  "con_inadmissible_categorical", "SummaryTable", "### Inadmissible Categorical Values of %s", "table",
  "con_hard_limits", "SummaryPlotList", "### Hard Limit Deviations Plots for %s",            "mv",
  "con_soft_limits", "SummaryPlotList", "### Soft Limit Deviations Plots for %s",            "mv",
  "con_detection_limits", "SummaryPlotList", "### Detection Limit Deviations Plots for %s",            "mv",
#  "con_contradictions", "SummaryPlot", "### Contradictions Affecting %s", NULL,
  "acc_distributions",    "SummaryPlotList", "### Distribution Plots for %s",                "mv",
#  "acc_distributions",    "SummaryPlotList", "### Distribution Plots for %s",                "plotlist_not_mv",
  "acc_shape_or_scale",   "SummaryPlot",     "### Distribution Shape-or-Scale Plots for %s", NULL,
  "acc_margins",          "SummaryPlot",     "### Marginal Means Plots for %s",              NULL,
  "acc_loess",            "SummaryPlotList", "### LOESS-smoothed Time Course Plots for %s",  "mv",
#  "com_unit_missingness", "SummaryPlot", "### Unit Missingngess", NULL,
#  "com_segment_missingness", "SummaryPlot", "### Segment Missingness", NULL,
#  "com_item_missingness", "SummaryPlot", "### Item Missingngess", NULL,
  "acc_univariate_outlier", "SummaryPlotList", "### Univariate Outlier of %s", "mv",
  "acc_varcomp", "SummaryTable", "### Variance Components of %s", "table",
  "acc_end_digits", "SummaryPlot", "### End digit preferences of %s", NULL,
#  "acc_multivariate_outlier", "SummaryPlot", "### acc_multivariate_outlier", NULL,
)
if (params$debug) {
  call_plan <- dplyr::tribble(
    ~ iform, ~ outputSlot, ~ title, ~ subreport,
  "acc_varcomp", "SummaryTable", "### Variance Components of %s", "table",
  )
}
invisible(NULL)
```

# Overview {data-navmenu="General information"}

> Analysing a data set with `r nrow(report$study_data)` observations and `r ncol(report$study_data)` variables. 
> The metadata table comprises `r ncol(report$meta_data)` attributes of `r nrow(report$meta_data)` variables.

```{r results='asis'}
if (!is.null(report$meta_data_dataframe)) {
  cat(sprintf("> Metadata on data frame level was provided with %d data frames and %d data frame attributes\n\n",
              nrow(report$meta_data_dataframe),
              ncol(report$meta_data_dataframe)))
}
```

```{r results='asis'}
if (!is.null(report$meta_data_segment)) {
  cat(sprintf("> Metadata on segment frame level was provided with %d segments and %d study segment attributes\n\n",
              nrow(report$meta_data_segment),
              ncol(report$meta_data_segment)))
}
```


```{r summary}
s <- summary(report)
hover <- s
hover[is.na(s)] <- "grey"
hover[hover == 1] <- "red"
hover[hover == 0] <- "green"
sv <- s$StudyVariable
for (cl in colnames(s)) {
  s[[cl]] <- 
    paste0("<span title=\"", 
            util_html_attr_quote_escape(htmltools::htmlEscape(hover[[cl]])),
           "\" style=\"display: inline-block;width:100%;background-color:",
            htmltools::htmlEscape(hover[[cl]]),
           "\">",
            htmltools::htmlEscape(s[[cl]]),
            "</span>")
}
if (nrow(s) > 0)
  s$StudyVariable <- paste0('<a href="#', prep_link_escape(sv, html = FALSE), '">', s$StudyVariable, '</a>')
s[is.na(s)] <- "N/A"
util_html_table(s, filter = "top", options = list(scrollCollapse = TRUE, scrollY = "75vh"), is_matrix_table = TRUE, rotate_headers = TRUE, output_format = "RMD")
```

# Metadata on variable (data element) level {data-navmenu="General information"}

```{r meta_data, echo=FALSE}
md <- report$meta_data
util_html_table(md, filter = "top", options = list(scrollCollapse = TRUE, scrollY = "75vh"), output_format = "RMD")
```

# Metadata on data frame (table) level {data-navmenu="General information"}
```{r meta_data_dfr, echo=FALSE, include=!is.null(report$meta_data_dataframe)}
md <- report$meta_data_dataframe
util_html_table(md, filter = "top", options = list(scrollCollapse = TRUE, scrollY = "75vh"), output_format = "RMD")
```

```{markdown no_meta_data_dfr, include=is.null(report$meta_data_dataframe)}
***ot provided.***
```

# Metadata on segment level {data-navmenu="General information"}
```{r meta_data_seg, echo=FALSE, include=!is.null(report$meta_data_segment)}
md <- report$meta_data_segment
util_html_table(md, filter = "top", options = list(scrollCollapse = TRUE, scrollY = "75vh"), output_format = "RMD")
```

```{markdown no_meta_data_seg, include=is.null(report$meta_data_segment)}
***Not provided.***
```

# Applicability figure {data-navmenu="General information"}
```{r app_mat, fig.height = 12, fig.width = 8}
print(report$app_mat$ApplicabilityPlot, dt = TRUE)
```

# Applicability matrix {data-navmenu="General information"}

```{r app_mat2}
s <- summary(report, aspect = "applicability", return_the_value = FALSE)
hover <- summary(report, aspect = "applicability", return_the_value = TRUE)
sv <- s$StudyVariable
for (cl in colnames(s)) {
  s[[cl]] <- 
    paste0("<span title=\"", 
            util_html_attr_quote_escape(htmltools::htmlEscape(hover[[cl]])),
           "\" style=\"display: inline-block;width:100%;background-color:",
            htmltools::htmlEscape(s[[cl]]),
           "\">",
            htmltools::htmlEscape(s[[cl]]),
            "</span>")
}
if (nrow(s) > 0)
  s$StudyVariable <- paste0('<a href="#', prep_link_escape(sv, html = FALSE), '">', s$StudyVariable, '</a>')
s[is.na(s)] <- "N/A"
util_html_table(s, filter = "top", options = list(scrollCollapse = TRUE, scrollY = "75vh"), is_matrix_table = TRUE, rotate_headers = TRUE, output_format = "RMD")
```

# Error matrix {data-navmenu="General information"}

```{r err_mat}
s <- summary(report, aspect = "error", return_the_value = FALSE)
hover <- summary(report, aspect = "error", return_the_value = TRUE)
sv <- s$StudyVariable
for (cl in colnames(s)) {
  s[[cl]] <- 
    paste0("<span title=\"", 
            util_html_attr_quote_escape(htmltools::htmlEscape(hover[[cl]])),
           "\" style=\"display: inline-block;width:100%;background-color:",
            htmltools::htmlEscape(s[[cl]]),
           "\">",
            htmltools::htmlEscape(s[[cl]]),
            "</span>")
}
if (nrow(s) > 0)
  s$StudyVariable <- paste0('<a href="#', prep_link_escape(sv, html = FALSE), '">', s$StudyVariable, '</a>')
s[is.na(s)] <- "N/A"
util_html_table(s, filter = "top", options = list(scrollCollapse = TRUE, scrollY = "75vh"), rotate_headers = TRUE, is_matrix_table = TRUE, output_format = "RMD")
```

# Data type missmatch {data-navmenu="Integrity"}
```{r int_dt_mat, fig.height = 12, fig.width = 8}
print(report$long_format$int_datatype_matrix$results[[1]]$ReportSummaryTable, dt = TRUE)
```

```{r IntSeg, results='asis'}
SegmentData <- 
  try(report$long_format$int_all_datastructure_segment$results[[1]]$SegmentData, 
      silent = TRUE)
if (!inherits(SegmentData, "try-error")) {
  for (indi in names(SegmentData)) {
    cat("\n# Segment: ", prep_title_escape(indi, html = FALSE), " {#", prep_link_escape(paste0("seg_", indi), html = FALSE), " data-navmenu=\"Integrity\"}\n\n", sep = "")
    tl <- htmltools::tagList(util_html_table(SegmentData[[indi]], filter = "top", options = list(scrollCollapse = TRUE, scrollY = "75vh"), output_format = "RMD"))
    tl[[1]]$height <- "auto"
    tl[[1]]$width <- "auto"
    cat(as.character(tl), sep = "\n")
  }
}
#SegmentTable <- try(report$long_format$int_all_datastructure_segment$results[[1]]$SegmentTable, silent = TRUE)
#if (is.data.frame(SegmentTable)) {
#  asis_output("# xxx")
#  util_html_table(SegmentTable, filter = "top", options = list(scrollCollapse = TRUE, scrollY = "75vh"), output_format = "RMD") # TODO: Colukn title mapping
#}
```

```{r IntDf, results='asis'}
DataframeData <- 
  try(report$long_format$int_all_datastructure_dataframe$results[[1]]$DataframeData, 
      silent = TRUE)
if (!inherits(DataframeData, "try-error")) {
  for (indi in names(DataframeData)) {
    cat("\n# Dataframe: ", prep_title_escape(indi, html = FALSE), " {#", prep_link_escape(paste0("dfr_", indi), html = FALSE), " data-navmenu=\"Integrity\"}\n\n", sep = "")
    tl <- htmltools::tagList(util_html_table(DataframeData[[indi]], filter = "top", options = list(scrollCollapse = TRUE, scrollY = "75vh"), output_format = "RMD"))
    tl[[1]]$height <- "auto"
    tl[[1]]$width <- "auto"
    cat(as.character(tl), sep = "\n")
  }
}
#DataframeTable <- try(report$long_format$int_all_datastructure_dataframe$results[[1]]$DataframeTable, silent = TRUE)
#if (is.data.frame(DataframeTable)) {
#  asis_output("# xxx")
#  util_html_table(DataframeTable, filter = "top", options = list(scrollCollapse = TRUE, scrollY = "75vh"), output_format = "RMD")
#}
```


# Unit missingness {data-navmenu="Completeness"}

```{r unit_miss_tab, fig.height = 12, fig.width = 8}
if (length(report$long_format$com_unit_missingness$results) >= 1)
  util_html_table(as.data.frame(t(report$long_format$com_unit_missingness$results[[1]]$SummaryData), stringsAsFactors = FALSE), filter = "top",
            options = list(scrollCollapse = TRUE, scrollY = "75vh"), output_format = "RMD")
```

# Segment missingness figure {data-navmenu="Completeness"}

```{r segment_miss_fig, fig.height = 12, fig.width = 8, error=TRUE}
if ((!is.null(report$long_format$com_segment_missingness)) && 
  (length(report$long_format$com_segment_missingness$results) == 1))
  if (inherits(report$long_format$com_segment_missingness$results[[1]], "try-error")) {
    stop(report$long_format$com_segment_missingness$results[[1]], call. = FALSE)
  } else {
    report$long_format$com_segment_missingness$results[[1]]$SummaryPlot
  }
```

# Segment missingness table {data-navmenu="Completeness"}

```{r segment_miss_tab, fig.height = 12, fig.width = 8, error=TRUE}
if (inherits(report$long_format$com_segment_missingness$results[[1]], "try-error")) {
  stop(report$long_format$com_segment_missingness$results[[1]], call. = FALSE)
} else {
  util_html_table(report$long_format$com_segment_missingness$results[[1]]$SummaryData, filter = "top", options = list(scrollCollapse = TRUE, scrollY = "75vh"), output_format = "RMD")
}
```

# Item missingness figure {data-navmenu="Completeness"}

```{r item_miss_fig, fig.height = 12, fig.width = 8, error=TRUE}
if (length(report$long_format$com_item_missingness$results) == 1) {
  if (inherits(report$long_format$com_item_missingness$results[[1]], "try-error")) {
    stop(report$long_format$com_item_missingness$results[[1]], call. = FALSE)
  } else {
    report$long_format$com_item_missingness$results[[1]]$SummaryPlot
  }
}
```

# Item missingness table {data-navmenu="Completeness"}

```{r item_miss_tab, fig.height = 12, fig.width = 8, error=TRUE}
if (inherits(report$long_format$com_item_missingness$results[[1]], "try-error")) {
  stop(report$long_format$com_item_missingness$results[[1]], call. = FALSE)
} else {
  util_html_table(report$long_format$com_item_missingness$results[[1]]$SummaryTable, filter = "top", options = list(scrollCollapse = TRUE, scrollY = "75vh"), output_format = "RMD")
}
```

# Inadmissible categorical values {data-navmenu="Consistency"}

```{r iac_tab, fig.height = 12, fig.width = 8, error=TRUE}
if (inherits(report$long_format$con_inadmissible_categorical$results[[1]], "try-error")) {
  stop(report$long_format$con_inadmissible_categorical$results[[1]], call. = FALSE)
} else {
  util_html_table(report$long_format$con_inadmissible_categorical$results[[1]]$SummaryTable, filter = "top", options = list(scrollCollapse = TRUE, scrollY = "75vh"), output_format = "RMD")
}
```

# Contradictions figure {data-navmenu="Consistency"}
```{r contra_fig, fig.height = 12, fig.width = 8}
if (length(report$long_format$con_contradictions$results) == 1)
  if (inherits(report$long_format$con_contradictions$results[[1]], "try-error")) {
    cat(conditionMessage(attr(report$long_format$con_contradictions$results[[1]], "condition")))
  } else {
    report$long_format$con_contradictions$results[[1]]$SummaryPlot
  }
```

# Contradictions table {data-navmenu="Consistency"}

```{r contra_tab, fig.height = 12, fig.width = 8}
progress(30)
if (inherits(report$long_format$con_contradictions$results[[1]], "try-error")) {
  cat(conditionMessage(attr(report$long_format$con_contradictions$results[[1]],
                        "condition")))
} else {
  util_html_table(report$long_format$con_contradictions$results[[1]]$SummaryData, 
            filter = "top", options = list(scrollCollapse = TRUE, scrollY = "75vh"), output_format = "RMD")
}
```

```{r con_output1, echo=FALSE, results='asis', eval = TRUE}
cp <- call_plan[startsWith(call_plan$iform, "con_"), , FALSE]
by_indicator <- dataquieR::prep_pmap(cp, function(...) {
  single_results <- 
    lapply(setNames(nm = unique(as.character(variables))), function(variable) {
    process_result_chunk(..., variable = variable, by_indicator = TRUE)
  })
  errors <- vapply(single_results, function(x) {
    inherits(x, "try-error") || inherits(x, "error")
  } , FUN.VALUE =  logical(1))
  if (any(errors)) {
    if (chunk_error) {
      invisible(lapply(single_results[errors], function(e) try(stop(e))))
    }
    single_results <- single_results[!errors]
  }
  if (all(vapply(single_results, inherits, "SummaryTable_by_indicator", 
                 FUN.VALUE = logical(1)))
      ) {
    single_results <- 
      single_results[vapply(single_results, length, FUN.VALUE = integer(1)) > 0]
    sr <- unlist(single_results, recursive = FALSE)
    single_errors <- vapply(sr, function(x) {
      w <- attr(x, "warning")
      if (chunk_warning) invisible(lapply(w, function(y) {try({attr(y, "condition")$call <- NULL}, silent = TRUE); try(warning(y))}))
      m <- attr(x, "message")
      if (chunk_message) invisible(lapply(m, function(y) try(message(y))))
      e <- attr(x, "error")
      if (chunk_error) invisible(lapply(e, function(y) {try({attr(y, "condition")$call <- NULL}, silent = TRUE); try(stop(y))}))
      length(e) > 0
    }, FUN.VALUE = logical(1))
    sr <- sr[!single_errors]
    oslo <- c(...)["outputSlot"] # oslo <- "SummaryTable" # for now only this
    if (all(vapply(lapply(sr, names), `%in%`, x = oslo, FUN.VALUE = logical(1)))) {
      sr <- lapply(sr, `[[`, oslo)
      srdf <- try(do.call(rbind.data.frame, sr), silent = TRUE)
      if (is.data.frame(srdf)) {
        tl <- htmltools::tagList(util_html_table(srdf, filter = "top", options = list(scrollCollapse = TRUE, scrollY = "75vh")), output_format = "RMD")
        tl[[1]]$height <- "auto"
        tl[[1]]$width <- "auto"
        single_results <- as.character(tl)
      }
    }
  }
  iform <- c(...)["iform"]
  title <- c(...)["title"]
  title <- gsub("^#+ ", "", title)
  title <- gsub(" [a-z]+ %s$", "", title)
  r <- c(sprintf('\n# %s {#%s_con_mv data-navmenu="Consistency"}', prep_title_escape(title, html = FALSE), 
                 iform), 
         single_results) 
  
  r[trimws(r) == ""] <- NULL
  progress(40)
  if (length(r) > 1) {
    r
  } else {
    NULL
  }
})
cat(unlist(by_indicator), sep = '\n')
names(by_indicator) <- cp$iform
if (chunk_error) {
  errors <- unlist(unlist(unlist(lapply(by_indicator, lapply, lapply, attr, "error"), recursive = FALSE), recursive = FALSE), recursive = FALSE)
  invisible(mapply(function(e, n) {
    n <- strsplit(n, ".", fixed = TRUE)[[1]]
    if (length(n) < 1) {
      n <- c("f", "v")
    } else if (length(n) < 2) {
      n <- c(n[[1]], n[[1]])
    }
    cond <- simpleError(conditionMessage(e), call(n[[1]], n[[2]]));
    try(stop(cond))
  }, e = errors, n = names(errors)))
}
if (chunk_warning) {
  errors <- unlist(unlist(unlist(lapply(by_indicator, lapply, lapply, attr, "warning"), recursive = FALSE), recursive = FALSE), recursive = FALSE)
  invisible(mapply(function(e, n) {
    n <- strsplit(n, ".", fixed = TRUE)[[1]]
    if (length(n) < 1) {
      n <- c("f", "v")
    } else if (length(n) < 2) {
      n <- c(n[[1]], n[[1]])
    }
    cond <- simpleWarning(conditionMessage(e), call(n[[1]], n[[2]])); 
    try(warning(cond))
  }, e = errors, n = names(errors)))
}
if (chunk_message) {
  errors <- unlist(unlist(unlist(lapply(by_indicator, lapply, lapply, attr, "message"), recursive = FALSE), recursive = FALSE), recursive = FALSE)
  invisible(mapply(function(e, n) {
    n <- strsplit(n, ".", fixed = TRUE)[[1]]
    if (length(n) < 1) {
      n <- c("f", "v")
    } else if (length(n) < 2) {
      n <- c(n[[1]], n[[1]])
    }
    cond <- simpleMessage(conditionMessage(e), call(n[[1]], n[[2]])); 
    try(message(cond))
  }, e = errors, n = names(errors)))
}
```
```{r con_output2, echo=FALSE, results='asis', eval = FALSE}
res <- lapply(unique(as.character(variables)), function(variable) {
    cp <- call_plan[startsWith(call_plan$iform, "con_"), , FALSE]
    cp$variable <- variable
    single_results <- dataquieR::prep_pmap(cp, process_result_chunk)
    errors <- vapply(single_results, function(x) {
      inherits(x, "try-error") || inherits(x, "error")
    } , FUN.VALUE =  logical(1))
    if (any(errors)) {
      if (chunk_error) {
        invisible(lapply(single_results[errors], function(e) try(stop(e))))
      }
      single_results <- single_results[!errors]
    }
    r <- c(sprintf('\n# %s {#%s_con data-navmenu="Consistency"}', dQuote(prep_title_escape(variable, html = FALSE)), prep_link_escape(variable, html = FALSE)), 
           single_results) 

    r[trimws(r) == ""] <- NULL
    if (length(r) > 1) {
      r
    } else {
      NULL
    }
  })
progress(50)
cat(unlist(res), sep = '\n')
```





```{r acc_output1, echo=FALSE, results='asis', eval = TRUE}
cp <- call_plan[startsWith(call_plan$iform, "acc_"), , FALSE]
by_indicator <- dataquieR::prep_pmap(cp, function(...) {
  single_results <- 
    lapply(setNames(nm = unique(as.character(variables))), function(variable) {
    process_result_chunk(..., variable = variable, by_indicator = TRUE)
  })
  errors <- vapply(single_results, function(x) {
    inherits(x, "try-error") || inherits(x, "error")
  } , FUN.VALUE =  logical(1))
  if (any(errors)) {
    if (chunk_error) {
      invisible(lapply(single_results[errors], function(e) try(stop(e))))
    }
    single_results <- single_results[!errors]
  }
  if (all(vapply(single_results, inherits, "SummaryTable_by_indicator", 
                 FUN.VALUE = logical(1)))
      ) {
    single_results <- 
      single_results[vapply(single_results, length, FUN.VALUE = integer(1)) > 0]
    sr <- unlist(single_results, recursive = FALSE)
    single_errors <- vapply(sr, function(x) {
      w <- attr(x, "warning")
      if (chunk_warning) invisible(lapply(w, function(y) {try({attr(y, "condition")$call <- NULL}, silent = TRUE); try(warning(y))}))
      m <- attr(x, "message")
      if (chunk_message) invisible(lapply(m, function(y) try(message(y))))
      e <- attr(x, "error")
      if (chunk_error) invisible(lapply(e, function(y) {try({attr(y, "condition")$call <- NULL}, silent = TRUE); try(stop(y))}))
      length(e) > 0
    }, FUN.VALUE = logical(1))
    sr <- sr[!single_errors]
    oslo <- c(...)["outputSlot"] # oslo <- "SummaryTable" # for now only this
    if (all(vapply(lapply(sr, names), `%in%`, x = oslo, FUN.VALUE = logical(1)))) {
      sr <- lapply(sr, `[[`, oslo)
      srdf <- try(do.call(rbind.data.frame, sr), silent = TRUE)
      if (is.data.frame(srdf)) {
        tl <- htmltools::tagList(util_html_table(srdf, filter = "top", options = list(scrollCollapse = TRUE, scrollY = "75vh")), output_format = "RMD")
        tl[[1]]$height <- "auto"
        tl[[1]]$width <- "auto"
        single_results <- as.character(tl)
      }
    }
  }
  iform <- c(...)["iform"]
  title <- c(...)["title"]
  title <- gsub("^#+ ", "", title)
  title <- gsub(" [a-z]+ %s$", "", title)
  r <- c(sprintf('\n# %s {#%s_acc_mv data-navmenu="Accuracy"}', prep_title_escape(title, html = FALSE), iform), 
         single_results) 
  
  r[trimws(r) == ""] <- NULL
  if (length(r) > 1) {
    r
  } else {
    NULL
  }
})
progress(65)
#save(by_indicator, file = "/tmp/xxx")
cat(unlist(by_indicator), sep = '\n')
names(by_indicator) <- cp$iform
if (chunk_error) {
  errors <- unlist(unlist(unlist(lapply(by_indicator, lapply, lapply, attr, "error"), recursive = FALSE), recursive = FALSE), recursive = FALSE)
  invisible(mapply(function(e, n) {
    n <- strsplit(n, ".", fixed = TRUE)[[1]]
    if (length(n) < 1) {
      n <- c("f", "v")
    } else if (length(n) < 2) {
      n <- c(n[[1]], n[[1]])
    }
    cond <- simpleError(conditionMessage(e), call(n[[1]], n[[2]])); 
    try(stop(cond))
  }, e = errors, n = names(errors)))
}
if (chunk_warning) {
  errors <- unlist(unlist(unlist(lapply(by_indicator, lapply, lapply, attr, "warning"), recursive = FALSE), recursive = FALSE), recursive = FALSE)
  invisible(mapply(function(e, n) {
    n <- strsplit(n, ".", fixed = TRUE)[[1]]
    if (length(n) < 1) {
      n <- c("f", "v")
    } else if (length(n) < 2) {
      n <- c(n[[1]], n[[1]])
    }
    cond <- simpleWarning(conditionMessage(e), call(n[[1]], n[[2]])); 
    try(warning(cond))
  }, e = errors, n = names(errors)))
}
if (chunk_message) {
  errors <- unlist(unlist(unlist(lapply(by_indicator, lapply, lapply, attr, "message"), recursive = FALSE), recursive = FALSE), recursive = FALSE)
  invisible(mapply(function(e, n) {
    n <- strsplit(n, ".", fixed = TRUE)[[1]]
    if (length(n) < 1) {
      n <- c("f", "v")
    } else if (length(n) < 2) {
      n <- c(n[[1]], n[[1]])
    }
    cond <- simpleMessage(conditionMessage(e), call(n[[1]], n[[2]])); 
    try(message(cond))
  }, e = errors, n = names(errors)))
}
```

```{r acc_output2, echo=FALSE, results='asis', eval = FALSE}
res <- lapply(unique(as.character(variables)), function(variable) {
    cp <- call_plan[startsWith(call_plan$iform, "acc_"), , FALSE]
    cp$variable <- variable
    single_results <- dataquieR::prep_pmap(cp, process_result_chunk)
    errors <- vapply(single_results, function(x) {
      inherits(x, "try-error") || inherits(x, "error")
    } , FUN.VALUE =  logical(1))
    if (any(errors)) {
      if (chunk_error) {
        invisible(lapply(single_results[errors], function(e) try(stop(e))))
      }
      single_results <- single_results[!errors]
    }
    r <- c(sprintf('\n# %s {#%s_acc data-navmenu="Accuracy"}', dQuote(prep_title_escape(variable, html = FALSE)), prep_link_escape(variabl, html = FALSE)), 
           single_results) 

    r[trimws(r) == ""] <- NULL
    if (length(r) > 1) {
      r
    } else {
      NULL
    }
  })
progress(85)
cat(unlist(res), sep = '\n')
```

```{r main_output, echo=FALSE, results='asis', eval = TRUE}
res <- lapply(unique(as.character(variables)), function(variable) {
    cp <- call_plan
    cp$variable <- variable
    single_results <- dataquieR::prep_pmap(cp, process_result_chunk)
    errors <- vapply(single_results, function(x) {
      inherits(x, "try-error") || inherits(x, "error")
    } , FUN.VALUE =  logical(1))
    if (any(errors)) {
      if (chunk_error) {
        invisible(lapply(single_results[errors], function(e) try(stop(, call. = FALSE))))
      }
      single_results <- single_results[!errors]
    }
    metamiss <- try(
      process_result_chunk("com_item_missingness", "", "### General Information about %s", "meta_miss", variable),
      silent = TRUE)
    if (inherits(metamiss, "try-error"))
      metamiss <- ""
    r <- c(list(sprintf('\n# %s {#%s data-navmenu="Single Variables"}', dQuote(prep_title_escape(variable, html = FALSE)), prep_link_escape(variable, html = FALSE))), 
           metamiss,
           single_results) 

    r[trimws(r) == ""] <- NULL
    if (length(r) > 1) {
      r
    } else {
      NULL
    }
  })
progress(99)
cat(unlist(res), sep = '\n')
```
