---
title: "dataquieR report"
author: "`r Sys.info()[['user']]`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  flexdashboard::flex_dashboard:
    storyboard: true
    vertical_layout: "scroll"
    orientation: "columns"
  html_document:
    toc: true
    toc_depth: 2
params:
  debug: false
---

```{css}
/*.chart-wrapper { overflow-x: scroll; }*/
```


```{r setup, include=FALSE}
if (params$debug) {
  template <- "default"
  packageName <- "dataquieR"
  chunk_echo <- FALSE
  chunk_warning <- FALSE
  chunk_error <- FALSE
  chunk_message <- FALSE
#  load("/tmp/report.RData")
}

variables <- report$app_mat$SummaryTable$Variables

df_report <- as.data.frame(report)
if (nrow(df_report) * ncol(df_report) == 0)
  stop("Report is empty, no results at all.")
library(DT)
knitr::opts_chunk$set(echo = chunk_echo, warning = chunk_warning, error = chunk_error, message = chunk_message)
cache <- new.env(parent = emptyenv())
process_result_chunk <- function(iform, outputSlot, title, subreport, variable) {
    subreport <- match.arg(subreport, c("", "mv", "table", "plotlist_not_mv"))
    if (nchar(subreport) > 0)
      subreport <- paste0("_", subreport)
    current_results <- subset(df_report, implementationform == iform, 'results', drop = TRUE)
    resp_vars <- subset(df_report, implementationform == iform, 'resp_vars', drop = TRUE)
    
    child_hash <-
      digest::digest(list(
        iform, outputSlot, title, subreport, variable
      ))
    
    if (exists(child_hash, cache)) {
      return(get(child_hash, cache))
    }
    
    chunk <- suppressWarnings(suppressMessages(try(
      knitr::knit_child(
        system.file(sprintf("%s_subreport%s.Rmd", template, subreport), package = packageName), 
        envir = environment(), 
        quiet = TRUE,
        options = list( # https://rdrr.io/github/rubenarslan/formr/man/asis_knit_child.html
           fig.path = paste0(knitr::opts_chunk$get("fig.path"), child_hash, "-"), 
           cache.path = paste0(knitr::opts_chunk$get("cache.path"), child_hash, "-")
        )
      ), 
    silent = TRUE)))
    
    assign(child_hash, chunk, cache)

    return(chunk)
}
call_plan <- dplyr::tribble(
  ~ iform, ~ outputSlot, ~ title, ~ subreport,
#  "con_inadmissible_categorical", "SummaryTable", "### Inadmissible Categorical Values of %s", "table",
  "con_limit_deviations", "SummaryPlotList", "### Hard Limit Deviations Plots for %s",            "mv",
  "con_detection_limits", "SummaryPlotList", "### Detection Limit Deviations Plots for %s",            "mv",
#  "con_contradictions", "SummaryPlot", "### Contradictions Affecting %s", NULL,
  "acc_distributions",    "SummaryPlotList", "### Distribution Plots for %s",                "mv",
  "acc_shape_or_scale",   "SummaryPlot",     "### Distribution Shape-or-Scale Plots for %s", NULL,
  "acc_margins",          "SummaryPlot",     "### Marginal Means Plots for %s",              NULL,
  "acc_loess",            "SummaryPlotList", "### LOESS-smoothed Time Course Plots for %s",  "plotlist_not_mv",
#  "com_unit_missingness", "SummaryPlot", "### Unit Missingngess", NULL,
#  "com_segment_missingness", "SummaryPlot", "### Segment Missingness", NULL,
#  "com_item_missingness", "SummaryPlot", "### Item Missingngess", NULL,
  "acc_univariate_outlier", "SummaryPlotList", "### Univariate Outlier of %s", "mv",
  "acc_varcomp", "SummaryTable", "### Variance Components of %s", "table",
  "acc_end_digits", "SummaryPlot", "### End digit preferences of %s", NULL,
#  "acc_multivariate_outlier", "SummaryPlot", "### acc_multivariate_outlier", NULL,
)
if (FALSE && params$debug) {
  call_plan <- dplyr::tribble(
    ~ iform, ~ outputSlot, ~ title, ~ subreport,
#  "con_inadmissible_categorical", "SummaryTable", "### Inadmissible Categorical Values of %s", "table",
  "con_limit_deviations", "SummaryPlotList", "### Hard Limit Deviations Plots for %s",            "mv",
  "con_detection_limits", "SummaryPlotList", "### Detection Limit Deviations Plots for %s",            "mv",
    "acc_varcomp",          "SummaryTable",    "### acc_varcomp",                 "table",
    "acc_margins",          "SummaryPlot",     "### Marginal Means Plots for %s", NULL,
    "acc_univariate_outlier", "SummaryPlotList", "### Univariate Outlier of %s", "mv",
    "acc_loess",            "SummaryPlotList", "### LOESS-smoothed Time Course Plots for %s",  "plotlist_not_mv",
  )
}
invisible(NULL)
```

# Overview {data-navmenu="General information"}

> Analysing a data set with `r nrow(report$study_data)` observations and `r ncol(report$study_data)` variables. 
> The metadata table comprises `r ncol(report$meta_data)` attributes of `r nrow(report$meta_data)` variables.

```{r summary}
s <- summary(report)
sv <- s$StudyVariable
for (cl in colnames(s)) {
  s[[cl]] <- htmltools::htmlEscape(s[[cl]])
}
if (nrow(s) > 0)
  s$StudyVariable <- paste0('<a href="#', sv, '">', s$StudyVariable, '</a>')
s[is.na(s)] <- "N/A"
datatable(s, filter = "top", escape=FALSE, )
```

# Applicability {data-navmenu="General information"}
```{r app_mat, fig.height = 12, fig.width = 8}
report$app_mat$ApplicabilityPlot
```

# Unit missingness {data-navmenu="Completeness"}

```{r unit_miss_tab, fig.height = 12, fig.width = 8}
if (length(report$long_format$com_unit_missingness$results) >= 1)
  datatable(as.data.frame(t(report$long_format$com_unit_missingness$results[[1]]$SummaryData), stringsAsFactors = FALSE), filter = "top")
```

# Segment missingness figure {data-navmenu="Completeness"}

```{r segment_miss_fig, fig.height = 12, fig.width = 8, error=TRUE}
if ((!is.null(report$long_format$com_segment_missingness)) && 
  (length(report$long_format$com_segment_missingness$results) == 1))
  if (inherits(report$long_format$com_segment_missingness$results[[1]], "try-error")) {
    stop(report$long_format$com_segment_missingness$results[[1]])
  } else {
    report$long_format$com_segment_missingness$results[[1]]$SummaryPlot[[1]]
  }
```

# Segment missingness table {data-navmenu="Completeness"}

```{r segment_miss_tab, fig.height = 12, fig.width = 8, error=TRUE}
if (inherits(report$long_format$com_segment_missingness$results[[1]], "try-error")) {
  stop(report$long_format$com_segment_missingness$results[[1]])
} else {
  datatable(report$long_format$com_segment_missingness$results[[1]]$SummaryData, filter = "top")
}
```

# Item missingness figure {data-navmenu="Completeness"}

```{r item_miss_fig, fig.height = 12, fig.width = 8, error=TRUE}
if (length(report$long_format$com_item_missingness$results) == 1) {
  if (inherits(report$long_format$com_item_missingness$results[[1]], "try-error")) {
    stop(report$long_format$com_item_missingness$results[[1]])
  } else {
    report$long_format$com_item_missingness$results[[1]]$SummaryPlot
  }
}
```

# Item missingness table {data-navmenu="Completeness"}

```{r item_miss_tab, fig.height = 12, fig.width = 8, error=TRUE}
if (inherits(report$long_format$com_item_missingness$results[[1]], "try-error")) {
  stop(report$long_format$com_item_missingness$results[[1]])
} else {
  datatable(report$long_format$com_item_missingness$results[[1]]$SummaryTable, filter = "top")
}
```

# Inadmissible categorical values {data-navmenu="Consistency"}

```{r iac_tab, fig.height = 12, fig.width = 8, error=TRUE}
if (inherits(report$long_format$con_inadmissible_categorical$results[[1]], "try-error")) {
  stop(report$long_format$con_inadmissible_categorical$results[[1]])
} else {
  datatable(report$long_format$con_inadmissible_categorical$results[[1]]$SummaryTable, filter = "top")
}
```

# Contradictions figure {data-navmenu="Consistency"}
```{r contra_fig, fig.height = 12, fig.width = 8}
if (length(report$long_format$con_contradictions$results) == 1)
  if (inherits(report$long_format$con_contradictions$results[[1]], "try-error")) {
    conditionMessage(attr(report$long_format$con_contradictions$results[[1]], "condition"))
  } else {
    report$long_format$con_contradictions$results[[1]]$SummaryPlot
  }
```

# Contradictions table {data-navmenu="Consistency"}

```{r contra_tab, fig.height = 12, fig.width = 8}
if (inherits(report$long_format$con_contradictions$results[[1]], "try-error")) {
  conditionMessage(attr(report$long_format$con_contradictions$results[[1]], "condition"))
} else {
  datatable(report$long_format$con_contradictions$results[[1]]$SummaryData, filter = "top")
}
```

```{r con_output1, echo=FALSE, results='asis', eval = TRUE}
cp <- call_plan[startsWith(call_plan$iform, "con_"), , FALSE]
by_indicator <- dataquieR::prep_pmap(cp, function(...) {
  single_results <- 
    lapply(setNames(nm = unique(as.character(variables))), function(variable) {
    process_result_chunk(..., variable = variable)
  })
  errors <- vapply(single_results, function(x) {
    inherits(x, "try-error") || inherits(x, "error")
  } , FUN.VALUE =  logical(1))
  if (any(errors)) {
    if (chunk_error) {
      invisible(lapply(single_results[errors], function(e) try(stop(e))))
    }
    single_results <- single_results[!errors]
  }
  iform <- c(...)["iform"]
  title <- c(...)["title"]
  title <- gsub("^#+ ", "", title)
  title <- gsub(" [a-z]+ %s$", "", title)
  r <- c(sprintf('\n# %s {#%s_con_mv data-navmenu="Consistency"}', title, iform), 
         single_results) 
  
  r[trimws(r) == ""] <- NULL
  if (length(r) > 1) {
    r
  } else {
    NULL
  }
})
cat(unlist(by_indicator), sep = '\n')
```
```{r con_output2, echo=FALSE, results='asis', eval = TRUE}
res <- lapply(unique(as.character(variables)), function(variable) {
    cp <- call_plan[startsWith(call_plan$iform, "con_"), , FALSE]
    cp$variable <- variable
    single_results <- dataquieR::prep_pmap(cp, process_result_chunk)
    errors <- vapply(single_results, function(x) {
      inherits(x, "try-error") || inherits(x, "error")
    } , FUN.VALUE =  logical(1))
    if (any(errors)) {
      if (chunk_error) {
        invisible(lapply(single_results[errors], function(e) try(stop(e))))
      }
      single_results <- single_results[!errors]
    }
    r <- c(sprintf('\n# %s {#%s_con data-navmenu="Consistency"}', dQuote(variable), variable), 
           single_results) 

    r[trimws(r) == ""] <- NULL
    if (length(r) > 1) {
      r
    } else {
      NULL
    }
  })
cat(unlist(res), sep = '\n')
```





```{r acc_output1, echo=FALSE, results='asis', eval = TRUE}
cp <- call_plan[startsWith(call_plan$iform, "acc_"), , FALSE]
by_indicator <- dataquieR::prep_pmap(cp, function(...) {
  single_results <- 
    lapply(setNames(nm = unique(as.character(variables))), function(variable) {
    process_result_chunk(..., variable = variable)
  })
  errors <- vapply(single_results, function(x) {
    inherits(x, "try-error") || inherits(x, "error")
  } , FUN.VALUE =  logical(1))
  if (any(errors)) {
    if (chunk_error) {
      invisible(lapply(single_results[errors], function(e) try(stop(e))))
    }
    single_results <- single_results[!errors]
  }
  iform <- c(...)["iform"]
  title <- c(...)["title"]
  title <- gsub("^#+ ", "", title)
  title <- gsub(" [a-z]+ %s$", "", title)
  r <- c(sprintf('\n# %s {#%s_acc_mv data-navmenu="Accuracy"}', title, iform), 
         single_results) 
  
  r[trimws(r) == ""] <- NULL
  if (length(r) > 1) {
    r
  } else {
    NULL
  }
})

cat(unlist(by_indicator), sep = '\n')
```

```{r acc_output2, echo=FALSE, results='asis', eval = TRUE}
res <- lapply(unique(as.character(variables)), function(variable) {
    cp <- call_plan[startsWith(call_plan$iform, "acc_"), , FALSE]
    cp$variable <- variable
    single_results <- dataquieR::prep_pmap(cp, process_result_chunk)
    errors <- vapply(single_results, function(x) {
      inherits(x, "try-error") || inherits(x, "error")
    } , FUN.VALUE =  logical(1))
    if (any(errors)) {
      if (chunk_error) {
        invisible(lapply(single_results[errors], function(e) try(stop(e))))
      }
      single_results <- single_results[!errors]
    }
    r <- c(sprintf('\n# %s {#%s_acc data-navmenu="Accuracy"}', dQuote(variable), variable), 
           single_results) 

    r[trimws(r) == ""] <- NULL
    if (length(r) > 1) {
      r
    } else {
      NULL
    }
  })
cat(unlist(res), sep = '\n')
```

```{r main_output, echo=FALSE, results='asis', eval = TRUE}
res <- lapply(unique(as.character(variables)), function(variable) {
    cp <- call_plan
    cp$variable <- variable
    single_results <- dataquieR::prep_pmap(cp, process_result_chunk)
    errors <- vapply(single_results, function(x) {
      inherits(x, "try-error") || inherits(x, "error")
    } , FUN.VALUE =  logical(1))
    if (any(errors)) {
      if (chunk_error) {
        invisible(lapply(single_results[errors], function(e) try(stop(e))))
      }
      single_results <- single_results[!errors]
    }
    r <- c(list(sprintf('\n# %s {#%s data-navmenu="Single Variables"}', dQuote(variable), variable)), 
           single_results) 

    r[trimws(r) == ""] <- NULL
    if (length(r) > 1) {
      r
    } else {
      NULL
    }
  })
cat(unlist(res), sep = '\n')
```
